An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
various formatting and minor edits

Recent years have seen an explosion of online services for learning
to program:  Udacity \cite{udacity}, Codecademy \cite{codeacademy},
ProgZoo \cite{progzoo}, 
Codingbat \cite{codingbat}, Coursera \cite{coursera}, Turingscraft
\cite{turingscraft}, Problets \cite{Kumar:2005:GPA:1163405.1163408}, CS Circles \cite{Pritchard:2013:CCI:2445196.2445370} and
several others.  These systems are very powerful, and show great promise to
improve introductory computer science.  Given all of these
very good systems, one may ask why we thought
%it a good career move
%to build yet another system.
the world needed another such system.

@@

CloudCoder is an open platform for managing short programming
exercises.
Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE \cite{Parlante:2013:NA:2445196.2445356}.

Figure~\ref{screenshot} shows a screenshot of a CloudCoder exercise.
The editor is derived from the Ace editor \cite{ace}, and supports
syntax high-lighting for most programming languages, and
auto-indentation.  
A submit button runs the code against a series of
test cases, and feedback is provided directly in the browser.
CloudCoder captures the code's standard output and
standard error streams to help students with debugging.

@@

We run Java code relatively securely under a Security Manager, and 
use Jython and JRuby to compile Python and Ruby to Java
bytecode, which we also run in a Security-Managed sandbox.  We
currently support C/C++ less securely, although 
recent work by Malan \cite{Malan:2013:CSS:2445196.2445242} on a
``sandbox'' for running untrusted student code can be leveraged to improve our security.

@@

One question is how to manage the data collected.  
Recent work on web-scale data collection by the BlueJ team
\cite{Utting:2012:WDG:2361276.2361278} lays out a number of important
questions about programming data, such as who should have access to the data, and what
mechanism should be used to access the data.  Sanders
et. al. \cite{Sanders:2008:DSE:1404520.1404534} reviewed a number of
the challenges involved in sharing empirical education data.

@@

{\bf Given an effective mechanism for sharing curriculum materials, could
courses at a number of institutions converge towards an optimum?}
This question is more philosophical, and is based on the observation that
curricula and pedagogy vary widely between instructors and institutions,
even for the ``same'' course \cite{Hertz:2010:CCM:1734263.1734335}.  We find ourselves wondering
if more effective ways ways of sharing curriculum materials would lead
to the best materials and ideas propagating widely, and if high-quality introductory
programming courses could created as a ``mash-up'' of materials created by
many authors at many institutions.  CloudCoder and similar systems
could be one mechanism enabling this type of transfer.

@@

Jadud's pioneering early work on novice compilation behavior
\cite{Jadud:2006:MTE:1151588.1151600}, along with follow-up work by
others \cite{Norris:2008:CCQ:1384271.1384284} provides a starting point for
work with program snapshots.

@@

Lane et. al. describe Intention-Based Scoring (IBS) \cite{Lane:2005:ISA:1047344.1047471},
an approach to building an ITS for programming whereby human
judges to score or code {\em charettes}, or assignments students work on in a
timed, closed-lab environment.  IBS derives from prior work on
identifying ``bugs'' in online protocols, and as such attempts to
identify places where students have a ``bug'' in their development
process.  This approach, while labor-intensive, shows some promise in
developing an ITS for programming assignments.

@@

The BlueJ team presents a compelling case for web-scale data
collection \cite{Utting:2012:WDG:2361276.2361278}.  Their system is
more ambitious than CloudCoder, but the data collected by CloudCoder
should be complementary.

>>>>

Recent years have seen an explosion of online services for learning
to program:  Udacity\cite{udacity}, Codecademy\cite{codeacademy},
ProgZoo\cite{progzoo}, 
Codingbat\cite{codingbat}, Coursera\cite{coursera}, CodeLab\cite{turingscraft},
Problets\cite{Kumar:2005:GPA:1163405.1163408}, CS Circles\cite{Pritchard:2013:CCI:2445196.2445370} and
several others.  These systems are very powerful, and show great promise to
improve introductory computer science.  Given all of these
very good systems, one may ask why we thought
%it a good career move
%to build yet another system.
the world needed another such system.

@@

CloudCoder is an open platform for managing short programming
exercises.
Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE\cite{Parlante:2013:NA:2445196.2445356}.

Figure~\ref{screenshot} shows a screenshot of a CloudCoder exercise.
CloudCoder uses the Ace editor\cite{ace}, which supports
syntax highlighting and automatic indentation for most programming languages.
The submit button runs the code against a series of
test cases. Once the test results are received, they are presented
directly in the browser, giving the student feedback on the
correctness of the submission.
CloudCoder captures the code's standard output and
standard error streams to help students with debugging.

@@

We run Java code relatively securely under a Security Manager, and 
use Jython and JRuby to compile Python and Ruby to Java
bytecode, which we also run in a Security-Managed sandbox.  We
currently support C/C++ less securely, although 
recent work by Malan\cite{Malan:2013:CSS:2445196.2445242} on a
``sandbox'' for running untrusted student code can be leveraged to improve our security.

@@

One question is how to manage the data collected.  
Recent work on web-scale data collection by the BlueJ team
\cite{Utting:2012:WDG:2361276.2361278} lays out a number of important
questions about programming data, such as who should have access to the data, and what
mechanism should be used to access the data.  Sanders
et. al.\cite{Sanders:2008:DSE:1404520.1404534} reviewed a number of
the challenges involved in sharing empirical education data.

@@

{\bf Given an effective mechanism for sharing curriculum materials, could
courses at a number of institutions converge towards an optimum?}
This question is more philosophical, and is based on the observation that
curricula and pedagogy vary widely between instructors and institutions,
even for the ``same'' course\cite{Hertz:2010:CCM:1734263.1734335}.  We find ourselves wondering
if more effective ways ways of sharing curriculum materials would lead
to the best materials and ideas propagating widely, and if high-quality introductory
programming courses could created as a ``mash-up'' of materials created by
many authors at many institutions.  CloudCoder and similar systems
could be one mechanism enabling this type of transfer.

@@

Jadud's pioneering early work on novice compilation behavior
\cite{Jadud:2006:MTE:1151588.1151600}, along with follow-up work by
others\cite{Norris:2008:CCQ:1384271.1384284} provides a starting point for
work with program snapshots.

@@

Lane et. al. describe Intention-Based Scoring (IBS)\cite{Lane:2005:ISA:1047344.1047471},
an approach to building an ITS for programming whereby human
judges to score or code {\em charettes}, or assignments students work on in a
timed, closed-lab environment.  IBS derives from prior work on
identifying ``bugs'' in online protocols, and as such attempts to
identify places where students have a ``bug'' in their development
process.  This approach, while labor-intensive, shows some promise in
developing an ITS for programming assignments.

@@

The BlueJ team presents a compelling case for web-scale data
collection\cite{Utting:2012:WDG:2361276.2361278}.  Their system is
more ambitious than CloudCoder, but the data collected by CloudCoder
should be complementary.
